Evidence of self-care tooling on digital video platforms and phylogenetic modelling reveal parrot tool use is not rare

### 2024-11-25 manuscript.Rmd
Update manuscript title

---
title             : "Evidence of self-care tooling on digital video platforms and phylogenetic modelling reveal parrot tool use is not rare"
shorttitle        : "Parrot tool use"

>>>>

---
title             : "New evidence of self-care tooling and phylogenetic modelling reveal parrot tool use is not rare"
shorttitle        : "Parrot tool use"
